Missing the Point$\colon$ Non-Convergence in Iterative Imputation Procedures

### 2020-04-22 3.Thesis/1.SimulationStudy/Writeup/manuscript.Rmd
Add diagram of steps in MI back in

>>>>

```{r}
# names <- c("A", "B", "C", "D", "E")
# M <- matrix(nrow = 6, ncol = 6, byrow = FALSE, data = 0)
# M[2, 3] <- M[3, 1] <- M[4, 2] <- M[4, 3] <- "flow"
# plotmat(M, curve = 0, name = names, lwd = 1, box.lwd = 2, cex.txt = 0.8, box.type = "circle", box.prop = 1.0)
# 
# M <- matrix(nrow = 6, ncol = 6, byrow = TRUE, data = c(
# # p n z d b f
# 0, 1, 0, 0, 0, 0, #p
# 0, 0, 4, 10, 11, 0, #n
# 2, 0, 0, 0, 0, 0, #z
# 8, 0, 13, 0, 0, 12, #d
# 9, 0, 0, 7, 0, 0, #b
# 0, 0, 5, 0, 0, 0 #f
# ))
# 
# 
# plotmat(M, pos = c(1, 2, 1, 2), curve = 0, name = names,
# lwd = 1, box.lwd = 2, cex.txt = 0.8,
# box.type = "square", box.prop = 0.5, arr.type = "triangle",
# arr.pos = 0.4, shadow.size = 0.01, prefix = "f",
# main = "NPZZDD model")
# #
# 
# library(diagram)
# data <- c(0, "'.47*'", 0,
#           0, 0, 0, 
#           "'.36*'", "'.33*'", 0)
# M<- matrix (nrow=3, ncol=4, byrow = TRUE, data=0)
# plot<- plotmat (M, 
#                 name= c( "Math self-efficacy","Math ability", "Interest in the math major"), 
#                 box.type = "rect", box.size = 0.12, box.prop=0.5,  curve=0)
# 
# library(semPlot)
# # A silly dataset:
# A <- B <- C <- D <- E <- F <- rnorm(10)
# DF <- data.frame(A, B, C, D, E, F)
# 
# # Two regressions:
# res1 <- lm(C ~ B, data = DF)
# res11 <- lm(D ~ B, data = DF)
# res12 <- lm(E ~ B, data = DF)
# res2 <- lm(A ~ B + C, data = DF)
# res3 <- lm(A ~ D + E + F, data = DF)
# 
# # Plot both in the same path diagram in two ways:
# semPaths(res1 + res2 + res3 + res11 + res12, "model", "est", intercepts = FALSE)
# semPaths(list(res1, res2), "model", "est", intercepts = FALSE)
```
